### 2021-04-14 Chapter-5/Chapter-5.tex
Updates from Overleaf

\begin{figure}[h]
  \begin{minipage}{0.4\linewidth}
    \resizebox{\linewidth}{!}{
      \begin{tikzpicture}
        [level distance=1cm,
          level 1/.style={sibling distance=2cm},
          level 2/.style={sibling distance=1.5cm}]
        \node {root}
        child {node {0}
            child {node {0:3}}
            child {node {1:4}}
          }
        child {node {1}
            child {node {0}}
            child {node {1:1}}
          };
      \end{tikzpicture}

    }\end{minipage}
  \hfill
  \begin{minipage}{0.18\linewidth}
    {
      \begin{lstlisting}[frame=none, numbers=none]
k1  00
k2  01
k3  01
k4  01
k5  00
k6  01
k7  11
k8  00
\end{lstlisting}
    }
  \end{minipage}
  \hfill
  \begin{minipage}{0.30\linewidth}
    \resizebox{\linewidth}{!}{

@@

\section{Implementation}
We have implemented a prototype of \ctool{}. It takes an input of ELF binary as well as the source code of the corresponding problem. The front-end of \ctool{} is implemented in Python. It can generate random inputs and test the program with those inputs many times.  The address record part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input. The main component uses libelfin, an open source library to parse ELF binaries and read DWARF debug information. The current implementation can support both 64-bits and 32-bits ELF binary in Linux. \ctool{} will be open-sourced.

@@

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Functions}} & \multicolumn{2}{c}{\textbf{Max. Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  4 KBs & 1 Byte  & 4 KBs & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Unsafe Password Checker& 65536& 16.0& 1&0&0&  0& 18 & 104 KB & 21 min & 0.4 min & 0 min\\
Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
One-byte Lookup Table & 65536 & 16.0& 1&1&0&  & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 65536 & 16.0& 1&1&0&  & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&0 &&& 1.1 MB &  \\
AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &&& 1.1 MB &  \\
AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &0&&& 1.0 MB   \\
AES  OpenSSL 1.1.1& 65536 & 16.0 & 2&0 &0&&& 909 KB\\
AES  wolfSSL 4.5.0& 65536 & 16.0 &2&0&0&  &&1.1 MB \\
AES Libgcrypt 1.8.7& 65536 & 16.0 &0 &0 &0& &&4.4 MB\\
RC4 mbedTLS 2.15& 65536 & 16.0 &2 &2 & & & & 1.1 MB\\
RC4 OpenSSL 1.1.0& 65536 & 16.0&2 &2 & & & & 1.0 MB\\
RC4 OpenSSL 1.1.1& 65536 & 16.0&2 &2 & & & & 896 KB\\
RC4 wolfSSL 4.5.0& 65536 & 16.0&2 &2 & & & &886 KB\\
RSA mbedTLS 2.15& 4096 & 12.0 &&&& &&1.8 MB\\
RSA OpenSSL 1.1.0& 4096 & 12.0 &&&& && 11 MB\\
RSA OpenSSL 1.1.1& 4096 & 12.0 &&&& &&13 MB\\
RSA wolfSSL 4.5.0& 4096 & 12.0 &&&& &&4.2 MB\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 &&&& &&4.4 MB\\
Tiny DNN & 12000 & 13.6 & &&&&& 4.4 MB \\
GDK 3.24.23 & 65535 & 16.0 & &&&&& 48 MB\\
\bottomrule
\end{tabular}
}

>>>>

\begin{figure}[h]
  \begin{minipage}{0.3\linewidth}
    \resizebox{\linewidth}{!}{
      \begin{tikzpicture}
        [level distance=1cm,
          level 1/.style={sibling distance=2cm},
          level 2/.style={sibling distance=1.5cm}]
        \node {root}
        child {node {0}
            child {node {0:3}}
            child {node {1:4}}
          }
        child {node {1}
            child {node {0}}
            child {node {1:1}}
          };
      \end{tikzpicture}

    }\end{minipage}
  \hfill
  \begin{minipage}{0.2\linewidth}
    {
      \begin{lstlisting}[frame=none, numbers=none]
k1  00
k2  01
k3  01
k4  01
k5  00
k6  01
k7  11
k8  00
\end{lstlisting}
    }
  \end{minipage}
  \hfill
  \begin{minipage}{0.25\linewidth}
    \resizebox{\linewidth}{!}{

@@

\section{Implementation}
We have implemented a prototype of \ctool{}. It takes an input of ELF binary as well as the source code of the corresponding problem. The front-end of \ctool{} is implemented in Python. It can generate random inputs and test the program with those inputs many times.  The address record part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input. The main component uses \textsf{libelfin}, an open source library to parse ELF binaries and read DWARF debug information. The current implementation can support both 64-bits and 32-bits ELF binary in Linux. \ctool{} will be open-sourced.

@@

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Functions}} & \multicolumn{2}{c}{\textbf{Max. Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  64 Bytes & 1 Byte  & 64 Bytes & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Unsafe Password Checker& 65536& 16.0& 1&0&0.04&  0& 18 & 104 KB & 21 min & 0.4 min & 0 min\\
Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
One-byte Lookup Table & 65536 & 16.0& 1&1&0&  & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 65536 & 16.0& 1&1&0&  & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&0 &&& 1.1 MB &  \\
AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &&& 1.1 MB &  \\
AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &0&&& 1.0 MB   \\
AES  OpenSSL 1.1.1& 65536 & 16.0 & 2&0 &0&&& 909 KB\\
AES  wolfSSL 4.5.0& 65536 & 16.0 &2&0&0&  &&1.1 MB \\
AES Libgcrypt 1.8.7& 65536 & 16.0 &0 &0 &0& &&4.4 MB\\
RC4 mbedTLS 2.15& 65536 & 16.0 &2 &2 & & & & 1.1 MB\\
RC4 OpenSSL 1.1.0& 65536 & 16.0&2 &2 & & & & 1.0 MB\\
RC4 OpenSSL 1.1.1& 65536 & 16.0&2 &2 & & & & 896 KB\\
RC4 wolfSSL 4.5.0& 65536 & 16.0&2 &2 & & & &886 KB\\
RSA mbedTLS 2.15& 4096 & 12.0 &&&& &&1.8 MB\\
RSA OpenSSL 1.1.0& 4096 & 12.0 &&&& && 11 MB\\
RSA OpenSSL 1.1.1& 4096 & 12.0 &&&& &&13 MB\\
RSA wolfSSL 4.5.0& 4096 & 12.0 &&&& &&4.2 MB\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 &&&& &&4.4 MB\\
Tiny DNN & 12000 & 13.6 & &&&&& 4.4 MB \\
GDK 3.24.23 & 65535 & 16.0 & &&&&& 48 MB\\
\bottomrule
\end{tabular}
}
